\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{charter}
% \usepackage[bitstream-charter]{mathdesign}
% {unset}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.125in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.185in]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}

  \textbf{\Huge 
  % \scshape
Owen Fahey} \\
  \small (310) 433-3042 $\cdot$
  \href{mailto:owenfahey@uchicago.edu}{\underline{owenfahey@uchicago.edu}} $\cdot$
  \href{https://www.linkedin.com/in/owen-fahey}{\underline{linkedin.com/in/owen-fahey}} $\cdot$
  \href{https://owenfahey.com}{\underline{owenfahey.com}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Chicago}{Chicago, IL}
      {Bachelor of Science in Computer Science \& Bachelor of Arts in Philosophy}{Expected June 2024}
      \resumeItemListStart
        \resumeItem{CS Major GPA: 3.9}
        \resumeItem {Specialization: Machine Learning}
        \resumeItem{{Selected Coursework:} Honors Algorithms, Computer Systems, Databases, Programming Languages, Discrete Math, Data Visualization, Data Science, Probability, Math for Machine Learning, Deep Learning Systems (TTIC)}
      \resumeItemListEnd
    \resumeSubheading
      {National Outdoor Leadership School}{Lander, WY}
      {Fall Semester in the Rockies}{August 2021 -- November 2021}
      \resumeItemListStart
        \resumeItem{Developed teamwork, leadership, and first responder skills on multiple wilderness expeditions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  {
    \vspace{-4pt}
    \noindent\hspace{0.15in}\small\textbf{Test Scores:} SAT: 1590, ACT: 36, American Invitational Math Exam Invitee (top 5\% of AMC 12 scores)
    \vspace{-5pt}
    }
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, JavaScript, TypeScript, C, Rust, HTML, CSS, Scala, SQL (Postgress)} \\
      \textbf{Python Libraries}{: OpenCV, NumPy, PIL, Matplotlib, scikit-learn, PyTorch, Flask, Django, bpy} \\
      \textbf{Web}{: React.js, Next.js, Node.js, D3.js, NPM, Apache, Web Components, Express.js, Three.js} \\
      \textbf{Other}{: Git, Github, Linux, FFmpeg, JSON, YAML, Bash, REST}}}
      {\vspace{-5pt}}
  \end{itemize}
  
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jason Salavon Studio}
      {Chicago, IL}
      {Software Developer}
      {June 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Spearheading system design and engineering on two art pieces created using in-house AI models, contributing 15k+ lines of code as the lead developer to the studio's codebase.}
        \resumeItem{Architecting an animation pipeline leveraging parallel computing, diffusion models, and GPT-3 API integration, enabling the production of massive animations with billions of pixels per frame.}
        \resumeItem{Collaborating with designers to quickly transform Figma mockups into functional software prototypes.}
        \resumeItem{Engineering a web application with a highly customized map interface using React.js, Leaflet, Apache, and Node.js that receives tens of thousands of  monthly visitors.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Chicago Computer Science Department}
      {Chicago, IL}
      {Research Assistant to Professor Gordon Kindlmann}
      {May 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Working to improve the effectiveness of data visualizations by accounting for differences in color perception.}
        \resumeItem{Devising numerical algorithms to create tailored, perceptually uniform color spaces by calibrating CIELAB models.}\resumeItem{Constructing an application for research studies to assess the efficacy of techniques aimed at rapidly and accurately modeling an individual's  perception of color.}
      \resumeItemListEnd
    \resumeSubheading
      {Lexset.ai}
      {Brooklyn, NY}
      {Software Engineering Intern}
      {January 2022 -- June 2022}
      \resumeItemListStart
        \resumeItem{Enhanced a Blender-based 3D scene and synthetic data generator with dozens of client-requested features.}
        \resumeItem{Secured firm's largest client by producing a tech demo dataset of 38,000 synthetic American Sign Language images.}\resumeItem{Automated HDRI classification and tagging, reducing processing time by 75\%.}
        \resumeItem{Monitored and debugged CoreWeave GPU instances ensuring optimal performance in machine learning workflows. }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}

\resumeSubHeadingListStart
      % \resumeProjectHeading
      %     {\textbf{Voxel Subdivider} $\cdot$ \emph{JavaScript, Three.js}}{\emph{September 2023}}
      %     \resumeItemListStart
      %       \resumeItem{Developed a web app to interactively subdivide a single voxel into an intricate voxel model.}
      %       \resumeItem{Implemented the logic to convert glTF 3D models into voxelized form.}
      %       \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Relational Database Storage Manager} $\cdot$ \emph{Rust}}{\emph{January 2023 -- March 2023}}
          \resumeItemListStart
             \resumeItem{Designed a functioning storage manager and slotted pages for a relational database using heap files.}
        \resumeItem{Implemented query operators such as AGGREGATE, GROUP BY, and JOIN from scratch.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Flight Delay Predictor} $\cdot$ \emph{Python, scikit-learn, Feature Engineering}}{\emph{September 2022}}
          \resumeItemListStart
            \resumeItem{Created a model to predict whether a flight was going to be delayed, achieving an AUC score of 0.74.}
            \resumeItemListEnd


    \resumeProjectHeading
          {\textbf{Music Overlap Analyzer} $\cdot$ \emph{Python, Flask, OAuth, scikit-learn}}{\emph{April 2022}}
          \resumeItemListStart
             \resumeItem{Developed an app to identify songs and artists mutually listened to by two users.}
            \resumeItem{Employed k-means clustering to generate a Spotify playlist based on overlapping musical preferences.}
          \resumeItemListEnd
\resumeSubHeadingListEnd

  
\end{document}